Template Master's Thesis

### 2023-08-21 paper.tex
Update discussion

%\textbf{Self-authorization}\\
Implementing the \textit{self-authorization} heuristic is straightforward, but results in very few identified address clusters. This is because it requires a highly specific on-chain behavior, which is rarely observed in practice. In particular, approvals are seldom used to authorize another externally owned account one might own. We also encountered a significant number of false-positives due to non-standard implementations. After excluding these instances, we identified a total of 15 entities consisting of 35 addresses. This outcome aligns with findings by \cite{FV:17}, who also observed that the heuristic captures only a small proportion of addresses. In his analysis of Ethereum transaction data up to block number 8,500,000 he identified 4,599 entities from 7,107 addresses.

%\textbf{Graph representation learning}\\

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.7\textwidth]{../figures/network_visualization_0xe2e.png}
	\caption{Token Transfer Graph for \texttt{0xE2e2F$\dots$faCa8}}
	\label{fig:cluster}
\end{figure}

%\textbf{LAND transfers}\\
The \textit{LAND transfer} heuristic is targeted at users revealing address clusters by sending high-value assets to other addresses. In this specific case, we use the information that all addresses are related to Decentraland and therefore analyze LAND transfers. However, the approach could be applied (more generally) to other NFT collections or large asset transfers in general. \newline
The main assumption behind this approach is that users may want to reorganize their accounts from time to time, mostly to increase security guarantees or spread the risk around multiple accounts. As a concrete example, some users may have started with a simple browser-based wallet but as the value of their assets increased and their knowledge grew, they changed to a more secure hardware wallet. We detect 161 entities with 413 addresses applying this approach. One cluster with 70 address is very likely a not a single entity. It includes an address that participated in the intial LAND auction and subsequently distributed LAND. This may have happened through off-chain compensation. The advantage of this method is that it is relatively easy to visualise and understand. The disadvantage is that it demands a specific on-chain behaviour and is only scalable with significant effort. Additionally, many events that occur off-chain are not detectable in the data, resulting in an increased occurrence of false positives.

%Moreover, when evaluating different network graphs as the starting point to create node embeddings we found better results in terms of average rank with the intra-set asset transfer dataset, instead of using all transfer events and/or transactions.
%740 transfers, 413 addressen und 161 or 160 entities with 342 addresses. -The large cluster may incorrectly be marked/maybe off-chain compensation? -> auction address
%%%%%%%%%%%%%%%%%%%%%

The goal of this research/thesis was to identify the number of entities represented by the 473,927 addresses observed in Decentraland between. By focusing on Ethereum and Polygon on-chain data, we narrowed down the address set to 137,544. Combining the three clustering heuristics applied, we successfully clustered 37.5\% (51,581) of these addresses into 29,680 entities. \newline
Assuming the remaining addresses each represent individual entities, we estimate a total of 115,643 active users during the studied time frame. Among them, 8,483 entities used more than one address, with the largest entity having 499 addresses. The distribution of cluster sizes can be seen in Figure \ref{fig:barplot_clusters}.

Assumptions: Assumptions: Role2Vec with a distance threshold of 0.5 (strict)
Removed large self-authorization cluster

Most clusters through graph representation learning
Very dependent on threshold
X \% use more than one address
Large address clusters could be some bot behavior

%Limitations: various assumptions, possibly false-positives, some clusters may well be undetected. 
%other Limitations -> ENS pairs? Incorporate time-of-day/normalized gas into feature vectors, two step approach
%Diskutiere alle resultate gemeinsam, vom anfangs set über on-chain und intra-set zu den clusters.

@@

Clustering heuristics -> specific on-chain events, user patterns, graph representation learning
Best -> graph representation learning
Combination as extension

1. Public blockchain -> all data available -> allows us to analyse it and find information
2. Clustering heuristics for account-based blockchains using on-chain data and on specific predefined address set
3. Most successful graph representation learning because does not require participation in specific on-chain event / usage pattern
4. From the various methods Role2Vec best
5. Summarize Final results
6. For researchers -> extend this approach -> apply it to other address sets -> package
7.

>>>>

Implementing the \textit{self-authorization} heuristic is straightforward, but results in very few identified address clusters. This is because it requires a highly specific on-chain behavior, which is rarely observed in practice. In particular, approvals are seldom used to authorize another externally owned account one might own. We also encountered a significant number of false-positives due to non-standard implementations. We are very confident that this cluster is not controlled by the same entity, and therefore remove it. After excluding these instances, we identified a total of 15 entities consisting of 35 addresses. This outcome aligns with findings by \cite{FV:17}, who also observed that the heuristic captures only a small proportion of addresses. In his analysis of Ethereum transaction data up to block number 8,500,000 he identified 4,599 entities from 7,107 addresses.

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.7\textwidth]{../figures/network_visualization_0xe2e.png}
	\caption{Token Transfer Graph for \texttt{0xE2e2F$\dots$faCa8}}
	\label{fig:cluster}
\end{figure}

%\textbf{LAND transfers}\\
The \textit{LAND transfer} heuristic is targeted at users revealing address clusters by sending high-value assets to other addresses. In this specific case, we use the information that all addresses are related to Decentraland and therefore analyze LAND transfers. However, the approach could be applied (more generally) to other NFT collections or large asset transfers in general. \newline
The main assumption behind this approach is that users may want to reorganize their accounts from time to time, mostly to increase security guarantees or spread the risk around multiple accounts. As a concrete example, some users may have started with a simple browser-based wallet but as the value of their assets increased and their knowledge grew, they changed to a more secure hardware wallet. We detect 161 entities with 413 addresses applying this approach. One cluster with 70 address is very likely a not a single entity. It includes an address that participated in the intial LAND auction and subsequently distributed LAND. This may have happened through off-chain compensation. The advantage of this method is that it is relatively easy to visualise and understand. The disadvantage is that it demands a specific on-chain behaviour and is only scalable with significant effort. Additionally, many events that occur off-chain are not detectable in the data, resulting in an increased occurrence of false positives. 
%740 transfers, 413 addressen und 161 or 160 entities with 342 addresses. -The large cluster may incorrectly be marked/maybe off-chain compensation? -> auction address

Ultimately, we combined the results for each clustering heuristic mentioned above. Consequently, we managed to cluster 51,518 addresses, corresponding to 29,680 distinct entities. When adding the unclustered addresses, we identified 115,643 active users during the nine months, with 8,483 entities interacting through multiple addresses. \newline
These results, however, are heavily influenced by the assumptions we made. We were conservative by setting a low distance threshold and treating all other addresses as individual entities. Raising the threshold would result in larger clusters and fewer entities. \newline 
The majority of addresses were clustered through graph representation learning methods. Unlike other clustering heuristics, this approach does not rely on specific on-chain behavior patterns or participation in particular events. Our implementation generally captures all addresses that have transferred within the address set at least once. Nevertheless, some clusters may still go undetected, while others may overestimate the number of addresses within a cluster. It is important to note that these methods are still only heuristics and testing the success on a large scale is not possible. \newline
Role2Vec performed very best for our small test sample, but is not necessarily always be superior to Diff2Vec or DeepWalk. Incorporating time-of-day and normalized gas into feature vectors, or refining clusters using a two-step approach, requires further research but could enhance clustering results.

@@

The goal of this research/thesis was to identify the number of entities represented by the 473,927 addresses observed in Decentraland between July 16, 2022 and April 23, 2023. By focusing on Ethereum and Polygon on-chain data, we narrowed the address set down to 137,544.

Clustering heuristics -> specific on-chain events, user patterns, graph representation learning
Best -> graph representation learning
Combination as extension
Approach, especially our node embedding implementation can be used and extended to cluster other predefined address set

1. Public blockchain -> all data available -> allows us to analyse it and find information
2. Clustering heuristics for account-based blockchains using on-chain data and on specific predefined address set
3. Most successful graph representation learning because does not require participation in specific on-chain event / usage pattern, sehr vielversprechend
4. From the various methods Role2Vec best
5. Summarize Final results
6. For researchers -> extend this approach -> apply it to other address sets -> add activity patterns ->
7. Sth about bots
8. Still a lot of natural activity on Decentraland and open infrastructure allows us to analyze it in detail as in this paper
